Compositional Certified Resource Bounds

### 2015-04-15 paper/main.tex
reordered the figures to fit page limit
edited caption of the big table

\begin{table*}
\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Experimental evaluation comparing the bounds generated KoAT, Rank,
  LOOPUS, SPEED, and our automatic amortized analysis on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize

>>>>

\begin{table*}
\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Comparison of the bounds generated by KoAT, Rank,
  LOOPUS, SPEED, and our tool $\toolname$ on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize
